An elementary and constructive proof of Grothendieck's generic freeness lemma

### 2018-05-16 paper-generic-freeness.tex
Added pointer to Richman's jewel

We remark that proof takes a somewhat curious course: Our goal is to
verify~$1 = 0$, but as an intermediate step we verify that~$M$ is free, which
after the fact will be a trivial statement.

@@

\printbibliography

>>>>

We remark that the proof takes a somewhat curious course: Our goal is to
verify~$1 = 0$, but as an intermediate step we verify that~$M$ is free, which
after the fact will be a trivial statement. This approach is reminiscient of
Richman's uses of trivial rings~\cite{richman:trivial-rings}.
\enlargethispage{1em}

@@

\nocite{blechschmidt:phd}
\printbibliography
